\documentclass{exam}
\usepackage{amsmath, amsfonts}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[super]{nth}

\DeclareMathOperator*{\argmin}{argmin}

\usepackage[hyperfootnotes=false]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\newcommand{\note}[1]{
	\noindent~\\
	\vspace{0.25cm}
	\fcolorbox{Red}{Orange}{\parbox{0.99\textwidth}{#1\\}}
	%{\parbox{0.99\textwidth}{#1\\}}
	\vspace{0.25cm}
}


\input{../macros.tex}
%\renewcommand{\hide}[1]{#1}

\qformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}
\bonusqformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}

\pagestyle{headandfoot}

%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%
\newcommand{\duedate}{31.05.19 (10:00)}
\newcommand{\due}{{\bf This assignment is due on \duedate.} }
\firstpageheader
{Due: \duedate \\ Points: 5}
{{\bf\lecture}\\ \assignment{5}}
{\lectors\\ \semester}

\runningheader
{Due: \duedate}
{\assignment{5}}
{\semester}
%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%

\firstpagefooter
{}
{\thepage}
{}

\runningfooter
{}
{\thepage}
{}

\headrule
\pointsinrightmargin
\bracketedpoints
\marginpointname{pt.}

\begin{document}
	\gccs
	Now that you have learned about evolutionary algorithms such as Differential Evolution (DE) you will implement the following yourself.
	\begin{questions}
		\titledquestion{Differential Evolution for HPO}[5]
		We provide you with the objective function to be optimized (see \texttt{src/main.py}). You will implement DE to \textbf{minimize} this function.
		\begin{parts}
		\part[3.5] Implement the evolutionary loop of DE which consists of initialization, mutation, crossover and selection operations. Use random initialization and a population size of 10 individuals (\i.e. $NP$=10). For the mutation and crossover rates, use $F$=0.5 and $CR$=0.5 respectively.\footnote{Hint: Your implementation of DE should perform boundary checking after mutation to be within the search range of the problem being solved (use random re-generation for that).}   
		\part[1.5] Generate plots that demonstrate the functionality of DE algorithm, e.g. best-so-far seen function value over time. Compare your results of DE against BO, Random Search and Gird Search for 100 function evaluations. Add all plots to a PDF and briefly discuss what you can learn from these plots, and add some observations about computational time for DE versus other compared optimizers.\footnote{Hint: Your implementation of DE should run for 20 generations.} 
	\end{parts}
		
		\titledquestion{Feedback}[Bonus: 0.5]
		For each question in this assignment, state:
		\begin{itemize}
			\item How long you worked on it.
			\item What you learned.
			\item Anything you would improve in this question if you were teaching the course.
		\end{itemize}
	\end{questions}
	
	\noindent
	\due Submit your solution for the tasks by uploading a PDF to your groups BitBucket repository. The PDF has to include the name of the submitter(s).
\end{document}