\documentclass{exam}
\usepackage{amsmath, amsfonts}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[super]{nth}

\DeclareMathOperator*{\argmin}{argmin}

\usepackage[hyperfootnotes=false]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\newcommand{\note}[1]{
	\noindent~\\
	\vspace{0.25cm}
	\fcolorbox{Red}{Orange}{\parbox{0.99\textwidth}{#1\\}}
	%{\parbox{0.99\textwidth}{#1\\}}
	\vspace{0.25cm}
}


\input{../macros}
%\renewcommand{\hide}[1]{#1}

\qformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}
\bonusqformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}

\pagestyle{headandfoot}

%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%
\newcommand{\duedate}{24.05.19 (10:00)}
\newcommand{\due}{{\bf This assignment is due on \duedate.} }
\firstpageheader
{Due: \duedate \\ Points: 5}
{{\bf\lecture}\\ \assignment{4}}
{\lectors\\ \semester}

\runningheader
{Due: \duedate}
{\assignment{4}}
{\semester}
%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%

\firstpagefooter
{}
{\thepage}
{}

\runningfooter
{}
{\thepage}
{}

\headrule
\pointsinrightmargin
\bracketedpoints
\marginpointname{pt.}

\begin{document}
	\gccs
	Now that you have learned about hyperparameter optimization techniques such as Bayesian optimization (BO) you will implement this loop yourself.
	\begin{questions}
		\titledquestion{Bayesian Optimization for HPO}[4]
		We provide you with a rough structure of the BO loop using a Gaussian Process. You will implement the remaining parts to \textbf{minimize} a synthetic 1D function.
		\begin{parts}
		\part[1] Implement the acquisition functions \textit{Expected Improvement} and \textit{Lower Confidence Bound}\footnote{Similar to \textit{Lower Confidence Bound}, but for minimizing an objective value} as presented in the lecture (use \texttt{NumPy} and \texttt{SciPy} wherever possible for efficiency). Keep in mind that you will use \texttt{scipy.minimize} to optimize the acquisition function.
		\part[1] Generate plots that demonstrate the functionality of the BO loop and of the implemented acquisition functions, e.g. best-so-far seen function value over time and the acquisition function values at different time steps. Add all plots to a PDF and briefly discuss what you can learn from these plots.
		\part[1] Implement Grid Search and Random Search.
		\part[1] Compare your implementations of BO against Random Search and Grid Search for at most 50 function evaluations\footnote{Hint: Your implementations of BO should perform better than Random Search.}
	\end{parts}
		
		\titledquestion{Feedback}[Bonus: 1]
		For each question in this assignment, state:
		\begin{itemize}
			\item How long you worked on it.
			\item What you learned.
			\item Anything you would improve in this question if you were teaching the course.
		\end{itemize}
	\end{questions}
	
	\noindent
	\due Submit your solution for the tasks by uploading a PDF to your groups BitBucket repository. The PDF has to include the name of the submitter(s).
\end{document}