\documentclass{exam}
\usepackage{amsmath, amsfonts}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[super]{nth}

\DeclareMathOperator*{\argmin}{argmin}

\usepackage[hyperfootnotes=false]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\newcommand{\note}[1]{
	\noindent~\\
	\vspace{0.25cm}
	\fcolorbox{Red}{Orange}{\parbox{0.99\textwidth}{#1\\}}
	%{\parbox{0.99\textwidth}{#1\\}}
	\vspace{0.25cm}
}


\input{../macros}
%\renewcommand{\hide}[1]{#1}

\qformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}
\bonusqformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}

\pagestyle{headandfoot}

%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%
\newcommand{\duedate}{17.05.19 (10:00)}
\newcommand{\due}{{\bf This assignment is due on \duedate.} }
\firstpageheader
{Due: \duedate \\ Points: 4}
{{\bf\lecture}\\ \assignment{3}}
{\lectors\\ \semester}

\runningheader
{Due: \duedate}
{\assignment{5}}
{\semester}
%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%

\firstpagefooter
{}
{\thepage}
{}

\runningfooter
{}
{\thepage}
{}

\headrule
\pointsinrightmargin
\bracketedpoints
\marginpointname{pt.}


\begin{document}
	\gccs
	Having learned about different ways to empirically evaluate the performances of algorithms and automl systems in this exercise you will now implement some of these techniques. Add your code creating plots and outputting statistics to \texttt{main.py} (callable as \verb|python main.py|). Furthermore, add all plots and answers to the questions to one PDF. Needless to say, that we expect all plots to have axes labels and a legend.
	\begin{questions}
		\titledquestion{Visualization and Evaluation}[3]
		\verb|data.csv| contains $n \times 2$ matrix with \textit{RMSE} score of two algorithms $A$ and $B$ on $n=419$ datasets. The method \verb|load_data()| loads this dataset as an $n \times 2$ \textit{numpy array}.
		\begin{parts}
			\part[1] Create a scatterplot comparing the performance of $A$ and $B$. Use different markers for the following three catgories of datasets:
			\begin{itemize}
				\item algorithm $A$ achieved an \textit{RMSE} value that is $0.1$ lower than that of $B$
				\item algorithm $B$ achieved an \textit{RMSE} value that is $0.1$ lower than that of $A$
				\item other
			\end{itemize}
			How many datasets are in each category? Report overall mean and standard deviation as well as median and quartile values for $A$ and $B$.
			\part[0.5] Plot the empirical distribution of $A$ an $B$ as shown in the lecture. 
			\part[0.5] Create a boxplot~\footnote{using \url{https://matplotlib.org/api/_as_gen/matplotlib.axes.Axes.violinplot.html}} and a violin plot~\footnote{using \url{https://matplotlib.org/api/_as_gen/matplotlib.pyplot.boxplot.html}} for $A$ and $B$. Write one sentence to describe the difference between these two kinds of plots.
			\part[0.5] Implement a paired permutation test. Using $H_0=$ $A$ and $B$ have equal menas, what are the test statistics with $10000$ repetitions? Would you reject $H_0$ with $\alpha=0.01$?
			\part[0.5] In the lecture you also learned about the $Z-test$ and the \textit{Wilcoxon rank-sum test}. Would it be valid to apply these tests for this dataset as well? \textbf{Briefly} justify you answer in two sentences.
		\end{parts}
	
	\titledquestion{Feedback}[Bonus: 1]
	For each question in this assignment, state:
	\begin{itemize}
	\item How long you worked on it.
	\item What you learned.
	\item Anything you would improve in this question if you were teaching the course.
	\end{itemize}
	\end{questions}
	
	\noindent
	\due Submit your solution for the tasks by uploading a PDF to your groups BitBucket repository. The PDF has to include the name of the submitter(s). Teams of at most $2$ students are allowed.
\end{document}