\section{Extensions}
\subsection{Noisy BO}
\begin{frame}{Extensions to BO}
\begin{block}{Standard BO Problem:}
\begin{itemize}
    \item Sequential optimization
    \pause
    \item Noise-free evaluations
    \item No constraints
\end{itemize}
\end{block}
\begin{block}{\emph{Exotic} BO Problem:}
\begin{itemize}
    \item Parallel evaluations
    \item Noisy evaluations
    \item Optimization with constraints
    \item Noisy constraints
\end{itemize}
\end{block}    
\end{frame}

\begin{frame}{Exotic BO Problem: Noisy Evaluations}
    \begin{itemize}
        \item Given noisy evaluations, GP regression proceeds similarly to the noiseless case.
        \begin{itemize}
            \item This is achieved by adding the noise variance terms in the diagonal of the covariance matrix of the GP.
        \end{itemize}
        \item Computing EI with observation noise is challenging.
        \begin{itemize}
            \item We no longer know the function value of the current best point $\cost^{*}$.
        \end{itemize}
        \item KG, ES, and PES apply directly in the setting with noise and retain one-step optimality properties.
        \end{itemize}
        \vspace{5mm}
        \center $\boobs_i=\cost(\conf_i)+\varepsilon_i$ where $\varepsilon\sim\normaldist(0,\tau_{i}^2)$
\end{frame}
%-----------------------------------------------------------------------
%\begin{frame}{Exotic BO Problem: Optimization with constraints}

%\center $\min\limits_{\conf}\cost(\conf)$ subject to $\constraintf_j(\conf)\leq %0, j=1,\dots,J$
%\pause


%\begin{block}{Noiseless constraints}
%\begin{itemize}
%   \item EI generalizes naturally to the constrained setting when $\cost$ and %$\constraintf_{i}$ are noiseless.
%   \pause
%  \item PES has been extended to predictive entropy search with constraints(PESC)
% \pause
%    \item KG has not been extended to constrained problems.
%    \pause
%\end{itemize}
%\end{block}
%\begin{block}{Noisy constraints}
%\begin{itemize}
%    \item EI is no longer analytic and requires integration over the posterior.
%    \pause
%    \item PESC can handle noise in constraints naturally.
%    \pause
%    \begin{itemize}
%        \item Requires difficult-to-implement approximations.
%    \end{itemize}
%\end{itemize}
%\end{block}
%\end{frame}
%-------------------------------------------------------------------------
\begin{frame}{Exotic BO Problem: Parallelization}
\begin{block}{Parallelization}
\begin{itemize}
    \item EI can be used for batch or asynchronous optimization by maximizing EI integrated over pending outcomes.
    \pause
    \item EI also can handle noise in batch optimization by integrating over samples from the EI posterior.
    \pause
    \item KG, ES and PES can also be extended to allow parallel function evaluations.
    \pause

\end{itemize}
\end{block}
\begin{itemize}
    \item Issue: BO underperforms on problems of high noise in the observations and constraints.
    \item Solution: EI under greedy batch optimization with noisy observations and constraints (NoisyEI)
\end{itemize}
    

\end{frame}
%----------------------------------------------------------------------------
\begin{frame}{Constrained Bayesian Optimization with Noisy Experiments}
\begin{itemize}
    \item GP priors for noisy function $\cost$:
    \begin{equation*}
        \cost^{n}|\dataset_{\cost} \sim \normaldist(\boldsymbol{\mean}_{\cost},\Sigma_{\cost})
    \end{equation*}
    \item Noisy Expected Improvement:
    \begin{equation*}
        \alpha_{NEI}(\conf|\dataset)=\int_{\cost^{n}}\alpha_{EIx}(\conf|\cost^{n})p(\cost^{n}|\dataset_{\cost})d\cost^{n}
    \end{equation*}
    \begin{itemize}
        \item NEI does not have an analytic expression, but it can be efficiently approximated using quasi-Monte Carlo approximation.
    \end{itemize}
\end{itemize}
    
\end{frame}

%----------------------------------------------------------------------
\begin{frame}{Constrained Bayesian Optimization with Noisy Experiments-Summary}
\begin{columns}[T] % align columns
\begin{column}{.48\textwidth}
    \begin{block}{Advantages}
    \begin{itemize}
    	\item Extending EI to scenarios of noisy, constrained problems.
    	\pause
    	\item 
    	\pause
    	\item ... 
    \end{itemize}
    \end{block}
\pause
\end{column}%

\hfill%

\begin{column}{.48\textwidth}

    \begin{block}{Disadvantages}
    \begin{itemize}
    	\item NEI relies on a large number of GPs, thus doesn't scale to large evaluation budgets.
    	\pause
    	\item ...
    \end{itemize}
\end{block}

\end{column}
\end{columns}   
\end{frame}

