\documentclass{exam}
\usepackage{amsmath, amsfonts}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[super]{nth}

\DeclareMathOperator*{\argmin}{argmin}

\usepackage[hyperfootnotes=false]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\newcommand{\note}[1]{
	\noindent~\\
	\vspace{0.25cm}
	\fcolorbox{Red}{Orange}{\parbox{0.99\textwidth}{#1\\}}
	%{\parbox{0.99\textwidth}{#1\\}}
	\vspace{0.25cm}
}


\input{macros}
%\renewcommand{\hide}[1]{#1}

\qformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}
\bonusqformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}

\pagestyle{headandfoot}

%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%
\newcommand{\duedate}{4.11.18 (14:00)}
\newcommand{\due}{{\bf This assignment is due on \duedate.} }
\firstpageheader
{Due: \duedate \\ Points: 4}
{{\bf\lecture}\\ \assignment{3}}
{\lectors\\ \semester}

\runningheader
{Due: \duedate}
{\assignment{3}}
{\semester}
%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%

\firstpagefooter
{}
{\thepage}
{}

\runningfooter
{}
{\thepage}
{}

\headrule
\pointsinrightmargin
\bracketedpoints
\marginpointname{pt.}


\begin{document}
	\gccs
	
	For this exercise assignment, 
	you are required to use the same ASlib scenarios as on the last sheet.
	Where necessary, you can also reuse code from the last exercise.
	\begin{questions}
		
		\titledquestion{Algorithm Selection}[4]
		
		Your task is to implement three of the presented algorithm selection approaches. You can choose between:
		
		\begin{itemize}
			\item regression model for each algorithm,
			\item pairwise regression models to predict the performance difference,
			\item cost-sensitive pairwise classification with voting,
			\item clustering,
			\item and $k$-nearest neighbour.
		\end{itemize} 
		
		For the underlying machine learning techniques, you should use again \texttt{sklearn},
		e.g., \texttt{sklearn.linear\_model.Ridge} for regression,
		\texttt{sklearn.ensemble.RandomForestClassifier} for classification,
		\texttt{sklearn.cluster.KMeans} for clustering
		and \texttt{sklearn.neighbors.KNeighborsClassifier} for kNN.
		
		To assess the performance of your algorithm selector,
		you should use the provided cross-validation splits in cv.arff.
		Accordingly, the call of your algorithm selector should look like this:
		
		\begin{verbatim}
		python aslib_selection.py --algoruns algorithm_runs.arff --features feature_values.arff\
		--cv cv.arff
		\end{verbatim}
		
		In the end, your algorithm selector should output the cross-validated PAR$10$ performance
		and the selected algorithm on each instance in the following format:
		
		\begin{verbatim}
		PAR10 performance: 1.2345
		Selection per instance:
		instance1.cnf, algo2
		instance2.cnf, algo3
		instance3.cnf, algo1
		...
		\end{verbatim}
		
		Please report the cross-validated performance ($\to$ PDF)
		and how you handled the hyper-parameters of your approach.
		We note that you will probably only get satisfactory results if you impute missing feature values (e.g., \texttt{sklearn.preprocessing.Imputer})
		and scale the instance features\\ (e.g., \texttt{sklearn.preprocessing.MinMaxScaler}) -- depending on your used approach.
		
		\titledquestion{Feedback}[Bonus: 1]
		For each question in this assignment, state:
		\begin{itemize}
			\item How long you worked on it.
			\item What you learned.
			\item Anything you would improve in this question if you were teaching the course.
		\end{itemize}
	\end{questions}
	
	\noindent
	\due Submit your solution for the tasks by uploading a PDF to your groups BitBucket repository. The PDF has to include the name of the submitter(s). Teams of at most $2$ students are allowed.
\end{document}