\documentclass{exam}
\usepackage{amsmath, amsfonts}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[super]{nth}

\DeclareMathOperator*{\argmin}{argmin}

\usepackage[hyperfootnotes=false]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\newcommand{\note}[1]{
	\noindent~\\
	\vspace{0.25cm}
	\fcolorbox{Red}{Orange}{\parbox{0.99\textwidth}{#1\\}}
	%{\parbox{0.99\textwidth}{#1\\}}
	\vspace{0.25cm}
}


\input{macros}
%\renewcommand{\hide}[1]{#1}

\qformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}
\bonusqformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}

\pagestyle{headandfoot}

%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%
\newcommand{\duedate}{18.11.18 (14:00)}
\newcommand{\due}{{\bf This assignment is due on \duedate.} }
\firstpageheader
{Due: \duedate \\ Points: 9}
{{\bf\lecture}\\ \assignment{5}}
{\lectors\\ \semester}

\runningheader
{Due: \duedate}
{\assignment{5}}
{\semester}
%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%

\firstpagefooter
{}
{\thepage}
{}

\runningfooter
{}
{\thepage}
{}

\headrule
\pointsinrightmargin
\bracketedpoints
\marginpointname{pt.}


\begin{document}
	\gccs
	
	Having learned about different ways to empirically evaluate the performances of algorithms you will have to implement some of these techniques to compare the performance of different configurations on provided data (\texttt{read\_data.py}). You will have to add your code to \texttt{main.py}, however if you run \texttt{python read\_data.py} you will be presented some statistics about the data.
	\begin{questions}
		\titledquestion{Empirical Evaluations}[9]
		We have provided you with data of 1000 configurations that have been evaluated on 604 instances and a script with which you can load the data in an easy to use format.
		\begin{parts}
			\part[1] Your first task is to implement a paired permutation test to determine if \texttt{conf\_0} and \texttt{conf\_1} have equal performance.
			\part[2] Complete \texttt{scatter\_and\_box} to compare both configurations using scatter plots and box plots. Timeouts should be highlighted in the scatter plot.
			\part[2] Implement the cdf-plots as presented in the lecture.
			\part[1] Complete \texttt{feature\_scatter} to visually determine if there are multiple clusters in the instance set. You are only required to scatter plot the data.
			\part[2] Add all plots (comparing \texttt{conf\_0} and \texttt{conf\_1}) to a pdf and \textit{interpret} the results.
		\end{parts}
	
	\titledquestion{Feedback}[Bonus: 1]
	For each question in this assignment, state:
	\begin{itemize}
	\item How long you worked on it.
	\item What you learned.
	\item Anything you would improve in this question if you were teaching the course.
	\end{itemize}
	\end{questions}
	
	\noindent
	\due Submit your solution for the tasks by uploading a PDF to your groups BitBucket repository. The PDF has to include the name of the submitter(s). Teams of at most $2$ students are allowed.
\end{document}