\documentclass{exam}
\usepackage{amsmath, amsfonts}
\usepackage{verbatim}
\usepackage{graphicx}
\usepackage[super]{nth}

\DeclareMathOperator*{\argmin}{argmin}

\usepackage[hyperfootnotes=false]{hyperref}

\usepackage[usenames,dvipsnames]{color}
\newcommand{\note}[1]{
	\noindent~\\
	\vspace{0.25cm}
	\fcolorbox{Red}{Orange}{\parbox{0.99\textwidth}{#1\\}}
	%{\parbox{0.99\textwidth}{#1\\}}
	\vspace{0.25cm}
}


\input{macros}
%\renewcommand{\hide}[1]{#1}

\qformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}
\bonusqformat{\thequestion. \textbf{\thequestiontitle}\hfill[\thepoints]}

\pagestyle{headandfoot}

%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%
\newcommand{\duedate}{12.01.19 (14:00)}
\newcommand{\due}{{\bf This assignment is due on \duedate.} }
\firstpageheader
{Due: \duedate \\ Points: 10}
{{\bf\lecture}\\ \assignment{9}}
{\lectors\\ \semester}

\runningheader
{Due: \duedate}
{\assignment{9}}
{\semester}
%%%%%% MODIFY FOR EACH SHEET!!!! %%%%%%

\firstpagefooter
{}
{\thepage}
{}

\runningfooter
{}
{\thepage}
{}

\headrule
\pointsinrightmargin
\bracketedpoints
\marginpointname{pt.}


\begin{document}
	\gccs
	After you now know how to use SMAC,
	your next task is to configure an algorithm of your own choice. This will enable you to use SMAC in your own projects
	
	\begin{questions}
		
		\titledquestion{Configuration of \textit{XYZ}}[Bonus: 9]
		The most demanding task in this exercise is to correctly define the configuration space. A quick explanation of the syntax of how to encode the configuration space
		to work with SMAC can be found here: \url{https://automl.github.io/SMAC3/stable/options.html#paramcs}\\
		You will have to define meaningful boundaries to keep the search space small enough such that SMAC does not have to deal with too many irrelevant values but large
		enough to not exclude good regions.
		
		For the remaining setup you can follow the previous exercise sheet.\\
		Briefly describe what algorithm you are optimizing, how your instances (if you have any) look like and how your derived your search space.
		Reuse the plotting code you implemented to compare your optimized configuration to the default configuration you started from.
		
		If you don't have an algorithm you want to optimize in mind, you can optimize any \texttt{sklearn} model on any of the \texttt{sklearn} datasets\footnote{\url{http://scikit-learn.org/stable/datasets/index.html}}. As instances you will have to draw 100 random splits of the dataset you choose to configure the model on.
		
		\titledquestion{Feedback}[Bonus: 1]
		For each question in this assignment, state:
		\begin{itemize}
			\item How long you worked on it.
			\item What you learned.
			\item Anything you would improve in this question if you were teaching the course.
		\end{itemize}
	\end{questions}

\noindent
\due Submit your solution for the tasks by uploading a PDF to your groups BitBucket repository. The PDF has to include the name of the submitter(s). Teams of at most $2$ students are allowed.
\end{document}